NDNS multilevel LCA CW2CB2 or CW2CB3

### 2018-07-24 paper/Chapters/Chapter2.tex
aims and objectives

%-----------------------------------
%	SECTION 2
%-----------------------------------
\section{Latent class analysis (LCA)}\vspace{-0.3cm}

@@

\section{Multilevel latent class analysis (MLCA)}\vspace{-0.3cm}

@@

\section{Strategy}\vspace{-0.3cm}

@@

The number of classes in either level 1 were determined by 1) the evaluation of model fit indices, including the Akaike information criterion (AIC), Bayesian information criterion (BIC), adjusted Bayesian information criterion (aBIC) where smaller values indicate better, and entropy which is a statistic that summarizes latent class probabilities where values near 1 indicate better latent class separation; 2) the Lo-Mendell-Rubin Likelihood Ratio Test (LMR-LRT) \parencite{lo2001testing, nylund2007deciding} and the Bootstrap Likelihood ratio test (BS-LRT) \parencite{peel2000robust} which compare $q$ vs. $q-1$ class models, where $q$ is the number of latent classes and 3) pattern interpretability. In the step of performing multilevel LCA, where neither LMR-LRT nor BS-LRT were available, same rules of model fit indices and pattern interpretability were used to determine the optimal combination of latent classes in level 1 and level 2.

@@

>>>>

%-----------------------------------
%	SECTION 2
%-----------------------------------
\section{Latent Class Analysis (LCA)}\vspace{-0.3cm}

@@

\section{Multilevel Latent Class Analysis (MLCA)}\vspace{-0.3cm}

@@

\section{Strategy of conducting MLCA in the current analysis}\vspace{-0.3cm}

@@

The number of classes in either level 1 were determined by 1) the evaluation of model fit indices, including the Akaike information criterion (AIC), Bayesian information criterion (BIC), adjusted Bayesian information criterion (aBIC) where smaller values indicate better, and entropy which is a statistic that summarizes latent class probabilities where values near 1 indicate better latent class separation; 2) the Lo-Mendell-Rubin Likelihood Ratio Test (LMR-LRT) \parencite{lo2001testing, nylund2007deciding} which compare $q$ vs. $q-1$ class models, where $q$ is the number of latent classes and 3) pattern interpretability. In the step of performing multilevel LCA, where neither LMR-LRT nor BS-LRT were available, same rules of model fit indices and pattern interpretability were used to determine the optimal combination of latent classes in level 1 and level 2.

\section{Latent Class Growth Analysis (LCGA)}

@@

The NDNS RP participants were drawn from the UK Postcode Address File, a list of all the addresses in the UK. The addresses were clustered into Primary Sampling Units (PSUs)
